AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
tab contribs

The team members had different levels of experience on software
development for large and distributed free software projects
like Scilab or Mozilla. In this way, one month of training was
conducted by two experienced developers, teaching the basics of use of
development support tools like bugtrackers, programming languages,
version control systems, and build systems. After this period, a starter project
was proposed for new developers, namely to have an accepted patch or commit to
the official repository for a large and widely used free software app.
Developers passing the starter project would be deemed `initiated' and be
called a `Macambira' developer.  Table~\ref{tabela:contribuicoes} summarizes the
effective accepted contributions of each successfully initiated developer to
free software projects in 2011.

@@

\begin{table}
  \caption{Free and open software projects that received contributions
    from ``Macambiras''. On the first column we can see a list of
    applications of those projects. At right, the pseudonym of the
    ``Macambiras'' who sent \textit{commits} to the application. At
    ``Lab Macambira'', and at free software community in general, is a
    common practice to use pseudonym as identification.}
    \begin{tabular}{|l|l|}
        \hline
        Application           & ``Commiters''                       \\
        \hline \hline
        Mozilla Firefox       & daneoshiga, bzum                    \\
        Evince                & hick209, bzum, marcicano, mquasar   \\
        BePDF / Xpdf          & marcicano                           \\
        Ekiga                 & flecha                              \\
        Empathy               & fefo                                \\
        Lib Folks (Telepathy) & kamiarc                             \\
        Scilab                & v1z, humannoise                     \\
        VxL                   & v1z                                 \\
        ImageMagick           & v1z                                 \\
        OpenOffice            & hick209                             \\
        Puredata              & v1z, automata, greenkobold, gilson, bzum \\
        Puredata OpenCV       & v1z                                 \\
        Puredata GEM          & v1z, fefo, hick209                  \\
        Puredata PDP          & v1z, fefo, hick209                  \\
        ChucK                 & rfabbri, automata                   \\
        ChucK MiniAudicle     & rfabbri, automata                   \\
        WebRTC                & automata                            \\
        OSC-Web               & automata                            \\
        Web-PD-GUI            & automata                            \\
        Live-Processing       & automata                            \\
        ChucK-Wiimote         & automata                            \\
        Audiolet              & automata                            \\
        Extempore             & automata                            \\
        \hline
    \end{tabular}
    \label{tabela:contribuicoes}
\end{table}

>>>>

The team members had different levels of experience on software
development for large and distributed free software projects
like Scilab or Mozilla. In this way, one month of training was
conducted by two experienced developers, teaching the basics of use of
development support tools like bugtrackers, programming languages,
version control systems, and build systems. After this period, a starter project
was proposed for new developers, namely to have an accepted patch or commit to
the official repository for a large and widely used free software app.
Developers passing the starter project would be deemed `initiated' and be
called a `Macambira' developer.  Table~\ref{tabela:contribuicoes} summarizes the
effective accepted contributions of each successfully initiated developer to
free software projects in 2011, which used the AA methodology.

@@

\begin{table}
  \caption{Free and open software projects that received contributions
    from successfully initiated developers  or `macambiras' that worked under
    the AA methodology. The first column lists applications to which
    contributions were officially accepted and whose development process was
    performed and logged using AA. The second column shows the pseudonym of the
    ``Macambiras'' who sent \textit{commits} to the application. At
    Lab Macambira, and at the free software community at large, 
    It is
    common practice at Lab Macambira, and the free software community at large,
    to use pseudonyms as identification in order to enhance privacy in practice.}
    \begin{tabular}{|l|l|}
        \hline
        Application           & ``Commiters''                       \\
        \hline \hline
        Mozilla Firefox       & daneoshiga, bzum                    \\
        Evince                & hick209, bzum, marcicano, mquasar   \\
        BePDF / Xpdf          & marcicano                           \\
        Ekiga                 & flecha                              \\
        Empathy               & fefo                                \\
        Lib Folks (Telepathy) & kamiarc                             \\
        Scilab                & v1z, humannoise                     \\
        VxL                   & v1z                                 \\
        ImageMagick           & v1z                                 \\
        OpenOffice            & hick209                             \\
        Puredata              & v1z, automata, greenkobold, gilson, bzum \\
        Puredata OpenCV       & v1z                                 \\
        Puredata GEM          & v1z, fefo, hick209                  \\
        Puredata PDP          & v1z, fefo, hick209                  \\
        ChucK                 & rfabbri, automata                   \\
        ChucK MiniAudicle     & rfabbri, automata                   \\
        WebRTC                & automata                            \\
        OSC-Web               & automata                            \\
        Web-PD-GUI            & automata                            \\
        Live-Processing       & automata                            \\
        ChucK-Wiimote         & automata                            \\
        Audiolet              & automata                            \\
        Extempore             & automata                            \\
        \hline
    \end{tabular}
    \label{tabela:contribuicoes}
\end{table}
